---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AMRNetherland

<!-- badges: start -->

<!-- badges: end -->

The goal of AMRNetherland is to provide a suite of tools for analyzing and visualizing antimicrobial resistance (AMR) data specific to the Netherlands. 

 
This package includes functions to calculate the prevalence of resistance genes in percentage, filter and summarize data by city and province, and more. 

It is designed to help researchers and public health officials easily access and analyze AMR data to monitor trends, get the patient data and inform decision-making. 
 

## Installation

You can install the development version of AMRNetherland from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("MarianaMousa1/AMRNetherland")
```

## Example

This is a basic example which shows you how to solve a common problem:
 
Function: Load_metadata
 
```{r example1}
 
library(AMRNetherland)
 
## basic example code
 
metadata <- Load_metadata("./Data/metadata.txt")
 
head(metadata)
 
```
 
Function: calculate_resgene_prevalence
 
```{r example}
library(AMRNetherland)
## basic example code
  gene <- "blaZ_79"  # Vervang dit door het specifieke resistentiegen waarvan je de prevalentie wilt berekenen
 
  data <- read.csv2("./Data/metadata.txt")  # Vervang "jouw_data.csv" door de naam van je dataset
 
calculate_resgene_prevalence(gene, data)

```

 
Function: get_antibiotic_class
 
```{r example3}
library(AMRNetherland)
 
## basic example code
   zipcode <- "8071"  # Vervang dit door de werkelijke postcode
 
  year_of_birth <- 1959  # Vervang dit door het werkelijke geboortejaar
 
  data <- read.csv2("./Data/metadata.txt")  # Vervang "jouw_data.csv" door de naam van je dataset
  antibiotic_class <- get_antibiotic_class(zipcode, year_of_birth, data)
 
  print(antibiotic_class)

```

Function: get_date_info

 
```{r example4}
library(AMRNetherland)
## basic example code
 
 date <- 16-06-2023
 
   data <- read.csv2("./Data/metadata.txt")
get_date_info <- get_date_info(data, date)
head(get_date_info)

```

 
Function: plot_ab_reis
 
```{r example5}
library(AMRNetherland)
## basic example code
   data <- read.csv2("./Data/metadata.txt")
 plot_ab_resis(data)

```



In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
