---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

knitr::opts_chunk$set(echo = TRUE)
source("../R/calculate_resgene_prevalence.R")
source("../R/get_antibiotic_class.R")
source("../R/get_date_info.R")
source("../R/Load_metadata.R")
source("../R/plot_ab_resis.R")

devtools::load_all()
```



# Introduction

The goal of AMRNetherland is to provide a suite of tools for analyzing and visualizing antimicrobial resistance (AMR) data specific to the Netherlands. 
This package includes functions to calculate the prevalence of resistance genes in percentage, filter and summarize data by city and province, and more. 


# Preparation 

You can skip to [Cleaning the data](#cleaning-the-data) if you already have your own data ready.


## Needed R packages

As with many uses in R, we need some additional packages for AMR data analysis. Our package works closely together with the [`dplyr`](https://dplyr.tidyverse.org/) and [`ggplot2`](https://ggplot2.tidyverse.org) by RStudio.


```{r lib packages, message = FALSE, warning = FALSE, results = 'asis'}
library(dplyr)
library(ggplot2)
library(AMRNetherland)

# (if not yet installed, install with:)
# install.packages(c("dplyr", "ggplot2", "AMRNetherland"))
```

## Examples

This is a basic examples


Function Load_metadata: This function reads a CSV file from the specified path and returns the metadata.

### Load_metadata example

```{r example1}
library(AMRNetherland)
## basic example code
metadata <- Load_metadata("../Data/metadata.txt")
head(metadata)

```


## Function calculate_resgene_prevalence: This function calculates the prevalence of a specified resistance in the dataset

### calculate_resgene_prevalence example

```{r example2}
library(AMRNetherland)
## basic example code
  gene <- "blaZ_79"  # Vervang dit door het specifieke resistentiegen waarvan je de prevalentie wilt berekenen
  data <- read.csv2("../Data/metadata.txt")  # Vervang "jouw_data.csv" door de naam van je dataset

calculate_resgene_prevalence(gene, data)

```


## Function get_antibiotic_class: Function to retrieve the antibiotic class based on zip code and year of birth

### antibiotic_class example

```{r example3}
library(AMRNetherland)
## basic example code
   zipcode <- "8071"  # Vervang dit door de werkelijke postcode
  year_of_birth <- 1959  # Vervang dit door het werkelijke geboortejaar
  data <- read.csv2("../Data/metadata.txt")  # Vervang "jouw_data.csv" door de naam van je dataset

  antibiotic_class <- get_antibiotic_class(zipcode, year_of_birth, data)
  print(antibiotic_class)

```


## Function get_date_info: This function filters the dataset for a specific sampling date and returns the unique combination of city, state, and gender.

### get_date_info example
```{r example4}
library(AMRNetherland)
## basic example code
 date <- 16-06-2023
   data <- read.csv2("../Data/metadata.txt")
 get_date_info <- get_date_info(data, date)
head(get_date_info)

```


## Function plot_ab_reis: This function groups the data per province and counts the number of antibiotic resistance classes per province. It then creates a bar plot of the number of classes per province.

### plot_ab_resis example
```{r example5}
library(AMRNetherland)
## basic example code
   data <- read.csv2("../Data/metadata.txt")
 plot_ab_resis(data)
```

conclusion
This package is designed to help researchers and public health officials easily access and analyze and visualize AMR data to monitor trends in Netherland, get and compare the patient information.
----
